%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	10pt,
]{style} % Use the style class

\usepackage{ebgaramond}
\usepackage{hyperref} % Use the EB Garamond font

%------------------------------------------------

\name{Hugo Pereira}

\address{(+33) 6~$\cdot$~26~$\cdot$~29~$\cdot$~40~$\cdot$~12 \\ \texttt{hugo0807pereira@gmail.com}} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

\begin{center}
	\url{https://www.linkedin.com/in/hugopereira75/}
\end{center}

\begin{center}
	\textbf{Graduating student in 2026 from Université de Technologie de Compiegne seeking internship starting in early 2026.}
\end{center}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{Airbus Defence \& Space}{August 2023 - Present}{Apprenticeship - Software Engineer}{Paris, France}
		\item Enhanced and evolved a Model-Based Systems Engineering (MBSE) plugin on CAMEO software, implemented in Java and utilized by numerous Airbus engineers.
		\item Spearheaded Continuous Integration/Continuous Deployment (CI/CD) setup and oversight for the project, embracing DevOps practices with Jenkins, Docker, Git, Jira \& Confluence.
		\item Optimized MBSE system to precisely align with architect requirements, ensuring seamless MBSE utilization.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Kardham Digital}{September 2022 - August 2023}{Apprenticeship - Developer, Assistant Digital Project Manager}{Paris, France}
		\item Development of full-stack solutions using Python, HTML, CSS, JavaScript, C\#, Java, and Django REST API.
		\item Completion of projects for the Research \& Development department at Kardham (presence forecasting, IoT development, space optimization, building data analysis).
		\item Data analysis using SQL, Pandas, Streamlit, and Elasticsearch to provide building life statistics as well as customized graphs based on client requests.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Kardham Digital}{June 2022 - August 2022}{Internship - Assistant Digital Project Manager}{Paris, France}
		\item Participation (BUILT \& RUN) in the monitoring of IT projects (project management with SCRUM).
		\item Traveling to client locations throughout France to organize the deployment of IT infrastructure projects: installing routers, firewalls, switches, sensors, and connected lights.
		\item Administration of systems and hosting of websites/projects using Apache2 on Debian servers.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Université Paris Cité}{October 2022 - Present}{Fixed-term contract - Student Tutor}{Paris, France}
		\item Weekly classes and tutoring for the university's disability section.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	\textbf{Université de Technologie de Compiègne (UTC) - Sorbonne} \hfill \textit{June 2026} \\
	Master in Computer Science \\
	Overall GPA: 5/5 \\
	Specializing in OOP, Design, Algorithmics, Data Structures, Operations Research \& Combinatorial Optimization

	\textbf{Université Paris Cité} \hfill \textit{June 2023} \\
	Associate's Degree in Computer Science \\
	Valedictorian

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Computer Languages & Java, Swift, Objective-C, C\#, C, C++, Python, JS, HTML, CSS, VB .NET \\
		Protocols \& APIs & XML, JSON, REST \\
		Databases & MySQL, PostgreSQL, Oracle, ORM (Sequelize, Django...) \\
		Tools & Vim, Linux, Git, Docker, Jenkins, Jira, Confluence, Trello, Slack \\
	\end{tabular}

\end{rSection}

\end{document}
